### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@dd5b75b2340b0fe071253c8809c060f062871007 🚀

\begin{enumerate}
    \itemMetawebs, i.e.~networks of potential interactions within a
species pool, are a powerful abstraction to understand how large-scales
species interaction networks are structured.%
    \itemBecause metawebs are typically expressed at large spatial and
taxonomic scales, assembling them is a tedious and costly process;
predictive methods can help circumvent the limitations in data
deficiencies, by providing `draft' metawebs.%
    \itemOne way to improve the predictive ability is to maximize the
information used for prediction, by using graph embeddings rather than
the list of species interactions. Graph embedding is an emerging field
in machine learning that holds great potential for ecoloigcal problems.%
    \itemIn this perspective, we outline how the challenges associated
with infering metawebs line-up with the advantages of graph embeddings;
furthermore, because metawebs are inherently spatial objects, we discuss
how the choice of the species pool has consequences on the reconstructed
network, but also embeds hypotheses about which human-made boundaries
are ecologically meaningful.%
\end{enumerate}

>>>>

\begin{enumerate}
    \item Metawebs, i.e.~networks of potential interactions within a
species pool, are a powerful abstraction to understand how large-scales
species interaction networks are structured.%
    \item Because metawebs are typically expressed at large spatial and
taxonomic scales, assembling them is a tedious and costly process;
predictive methods can help circumvent the limitations in data
deficiencies, by providing `draft' metawebs.%
    \item One way to improve the predictive ability is to maximize the
information used for prediction, by using graph embeddings rather than
the list of species interactions. Graph embedding is an emerging field
in machine learning that holds great potential for ecoloigcal problems.%
    \item In this perspective, we outline how the challenges associated
with infering metawebs line-up with the advantages of graph embeddings;
furthermore, because metawebs are inherently spatial objects, we discuss
how the choice of the species pool has consequences on the reconstructed
network, but also embeds hypotheses about which human-made boundaries
are ecologically meaningful.%
\end{enumerate}
